%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Project Manager} % Job title
    {Synergy Technology Services} % Organization
    {Mumbai, India} % Location
    {June 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed an overall architecture, Managed development, registrations, offline and online payment gateway integration, center allotment, generation of hall tickets, server backend, database, reporting for end to end recruitment portal for Maharashtra State Road Transport Corporation.}
        \item {Built security into product to achieve 100\% compliance with STQC (Standardisation Testing and Quality Certification) and CERT-In.}
        \item {Developed custom installers to reduce manual software installation process for product by about 50\%.}
        \item {Developed Java based payment API for Instamojo Payment Gateway Solution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tech Lead} % Organization
    {Synergy Technology Services} % Organization
    {Mumbai, India} % Location
    {May 2010 - June 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated Spring Security for authentication process against LDAP and Database on DIMeX.}
        \item {Integrated Spring Mobile, redesigned user interfaces so that the application can be accessed on mobiles and tablets.}
        \item {Integrated BIRT report engine for PDF and Excel report generation. }
        \item {Implemented customizable charts using c3.js charting library.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {BNED LoudCloud Systems} % Organization
    {Mumbai, India} % Location
    {May 2013 - April 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and managed Flashcards. Includes features to create decks, create and add text/media based cards to decks, attempt decks in play and challenge modes etc.}
        \item {Developed and managed Learning Communities featuring groups, study circles, meeting rooms, events, chat etc.}
        \item {Developed Quiz Module featuring question bank, quizzes with various configuration options, ability for students to attempt quizzes, ability for instructors to grade students using Rubrics for particular competency/learning objective or criteria etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Deutsche Bank} % Organization
    {Mumbai, India} % Location
    {March 2012 - December 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an application for Headcount Management, Reporting and Reconciliation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Synergy Technology Services} % Organization
    {Mumbai, India} % Location
    {July 2007 - May 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented features for dealers of gpxtire.com to search tires, place orders, claim for warranty, send quotes etc.}
        \item {Developed an application for bcglogistics.com to manage and track their orders and shipments.}
        \item {Developed and managed Compliance Positioning System that allows company’s compliance staff to effortlessly track, correct, and record their organization’s compliance status by converting complex legislation and regulation into plain-language summaries, action-items, and questionnaires.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Software Engineer} % Job title
    {Rubicon Info Solutions} % Organization
    {Mumbai, India} % Location
    {Feb 2007 - July 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted development on online portal for buying and selling various products.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
